%\documentclass[12pt]{scrreprt}
\documentclass[12pt]{report} 

% language may be romanian or english (default is english)
% type may be bachelor or master (default is bachelor)
\usepackage[language=romanian, type=bachelor]{style}
%\geometry{a4paper,top=2.5cm,left=3cm,right=2.5cm,bottom=2.5cm}
%in style
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}
\usepackage{listing}
\usepackage{graphicx}
\usepackage{float}
\usepackage{gensymb}
\usepackage{subcaption}
\usepackage{url}
\pagestyle{fancy}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}

\begin{document}

\specialization{Informatică Română}
\title{Detectarea automată a numerelor de înmatriculare folosind tehnici clasice de viziune artificială și clasificatori statistici}
\author{Pușcaș Raul-Andrei}
\supervisor{Conferențiar, Dr. Bufnea Darius}
				
\maketitle


\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\pagenumbering{roman} 

\cleardoublepage
ABSTRACT
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

% Structura: Cuprins -> Introducere(approx 1 + 1/2 pagini, despre ce e lucrarea, de ce am abordat, importanta si cum am abordat  1/2 structura lucrarii in continuare) [Introducerea tradusa -> Abstract] -> Capitole Teoretice(fara cod) -> Capitole Tehnice(API, IoT devices, OpenCV, Aplicatii Existente etc.) -> Capitol pentru Aplicatie(Documentatie ISS, diagrame, actori) Subcapitol de testare -> Concluzii + Biografie

% Introducere approx 1 pagina (contextul aplicatiei, ce aduce in plus[ce fac, de ce fac, cum fac, cat de important e] <- partea I)
% Restul structurii pe capitole <- partea II TOT DIN INTRODUCERE

% Evidentierea ca primele 3 capitole sunt teoretice ( general -> specific ) + alt titlu

% Implementarea sistemului -> Nume mai specific, cu numele aplicatiei
% Subcapitol de testare -> metrici
% Subcapitol de experimente

% Numerele < 10 scrise cu litere

Automatic license plate recognition (ALPR) has become a core building block of intelligent
transportation systems, underpinning applications as diverse as traffic law enforcement,
electronic toll collection, stolen-vehicle detection and the management of restricted-access
areas such as parking facilities. At its essence, an ALPR system extracts a vehicle's unique
alphanumeric identifier from an image and converts it into machine-readable text, a task
that remains challenging under unconstrained conditions, owing to variations in illumination,
plate format, font, viewing angle and partial occlusions.
\paragraph{}
This thesis proposes such a system, named IORA, designed around a modular architecture and
relying solely on classical computer vision techniques for the image-processing stages and on
a statistical Support Vector Machine (SVM) classifier for character recognition. The work
targets a concrete deployment scenario, an automated access-control point for a parking
facility in Romania, which imposes two requirements: the robust handling of the many plate
formats in circulation, from standard and temporary plates to diplomatic and institutional
ones, and an execution time low enough to actuate the barrier within one to two seconds of a
vehicle's arrival.
\paragraph{}
Following the canonical ALPR pipeline, the system is organised into three sequential stages.
Plate localization combines the Sobel operator with morphological operations and geometric
filtering to isolate candidate regions; character segmentation separates the individual
symbols through contour analysis guided by a priori knowledge of plate geometry; and
recognition assigns a label to each character using a multi-class SVM trained on HOG
descriptors. By avoiding deep neural networks altogether, the pipeline is able to run on
modest hardware without GPU acceleration.
\paragraph{}
The system is evaluated both end-to-end and per stage, on a heterogeneous dataset spanning
Romanian and international plates. The results show that, when classical methods are guided by
domain-specific a priori knowledge, they remain a competitive and resource-efficient
alternative for real-time license plate recognition, while also exposing the limitations that
motivate further work.
\tableofcontents

\newpage
\pagenumbering{arabic}

\input{chapters/chapter1_introduction}
%\addcontentsline{toc}{chapter}{Introducere}
%\addcontentsline{toc}{chapter}{Introduction}

\input{chapters/chapter2}
\input{chapters/chapter3}
\input{chapters/chapter4}
\input{chapters/chapter5}
\input{chapters/chapter6_evaluation}
\input{chapters/chapter7_conclusions}
%\addcontentsline{toc}{chapter}{Concluzii}
%\addcontentsline{toc}{chapter}{Conclusions}
\bibliography{references}
\end{document}
